Efficient pedigree recording for fast population genetics simulation

### 2018-01-04 forwards_paper.tex
clarified horiz lines in fig 5

\begin{figure}
    \begin{center}
        \includegraphics{method_diagram}
    \end{center}
    \caption{
        A simple example of the simplify method.
        \textbf{Top:} the diagram on the left relates ten haploid individuals to each other.
        It has 10 node records (one for each individual)
        and 14 edge records (one for each distinctly inherited segment).
        Blue numbers denote crossing over locations in each meiosis --
        for instance, $C$ and $D$ were parents to $F$,
        who inherited the left 70\% of the chromosome from $D$ and the remainder from $C$.
        The individuals $B$, $C$, and $D$ inherit clonally from $A$.
        \textbf{Center:} the five distinct trees relating all individuals to each other
        found across the chromosome (blue numbers denote locations on the chromosome).
        Labels after simplification are shown in red.
        \textbf{Bottom:} tables recording the tree sequence after simplification
        with nodes $I$ and $J$ as samples.
        The mapping from labels in the forwards time simulation to nodes in the tree sequence
        is shown in red.
        % which allows additional records to be added as the simulation progresses.
        \label{fig:method_diagram}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{method_diagram}
    \end{center}
    \caption{
        A simple example of the simplify method.
        \textbf{Top:} the augmented pedigree diagram on the left 
        relates ten haploid ``individuals'' (i.e., parental chromosomes) to each other;
        dotted lines connect individuals who mate, and solid lines lead to their offspring.
        The corresponding tables (right) have 10 node records (one for each individual)
        and 14 edge records (one for each distinctly inherited segment).
        Blue numbers denote crossing over locations --
        for instance, $C$ and $D$ were parents to $F$,
        who inherited the left 70\% of the chromosome from $D$ and the remainder from $C$.
        Individuals $B$, $C$, and $D$ inherit clonally from $A$.
        \textbf{Center:} the five distinct trees
        found across the chromosome (blue numbers denote locations on the chromosome).
        Labels after simplification are shown in red.
        \textbf{Bottom:} tables recording the tree sequence after simplification
        with nodes $I$ and $J$ as samples.
        The mapping from labels in the forwards time simulation to nodes in the tree sequence
        is shown in red.
        % which allows additional records to be added as the simulation progresses.
        \label{fig:method_diagram}
    }
\end{figure}
